---
title: "Untitled"
author: "Mallek"
date: "December 2, 2014"
output: html_document
---


```{r}
ccavg.r3.samp = read.csv('/Users/mmallek/Tahoe/RMLands/results/results20150904/ccavg.r3_samp.csv')
#ccavg.r3.samp = read.csv('/Users/mmallek/Tahoe/RMLands/results/results20150904/ccavg_r3_50Gsmoothclip_samp.csv')
#ccavg.r3res.samp = read.csv('/Users/mmallek/Tahoe/RMLands/results/results20150904/ccavg_r3res_50Gsmoothclip_samp.csv')
data = ccavg.r3.samp
PlotLevels = unique(data$cover)
(PlotLevels = sort(PlotLevels))



```


This set of plots shows the simple regression line for TPI against Canopy Cover for each cover type individually.
```{r}
require(ggplot2)
require(grid)
# all the sampled data points
pl = ggplot(data, aes(x=tpi, y=ccavg)) + geom_point()
pl

# right now basically all the cover types are in, but I only want some of them

# each cover type separately (facet)
covertypes = c('CMM', 'LPN','LPN_ASP','MEG_M','MEG_U','MEG_X','MRIP',
               'OCFW','OCFW_U','RFR_ASP','RFR_M','RFR_U','RFR_X','SCN','SMC_ASP',
               'SMC_M','SMC_U','SMC_X',"WWP")

covers = as.data.frame(covertypes)
dict = as.data.frame(sort(unique(data$cover)))
names(dict) = "covcode"
#dict = dict[c(3,5,6,9:12,14:19,21,23:26,29),]
dict = as.data.frame(dict)

dict2 = cbind(dict, covers)
require(plyr)
dict2 = rename(dict2, c('covcode'='cover'))
#dict2 = rename(dict2, c('cover'='covcode'))
#data$covname = data$cover

#data2 <- match(data$covname, dict2$cover)
data2 = join(data, dict2, by = "cover")

pl5 = ggplot(data2, aes(x=tpi, y=ccavg)) + geom_point()
pl5 + facet_wrap(~covname, ncol= 4) + geom_smooth(method='lm') # works again! 2015-07-01


```
Note that cover types 3 and 6 (Curl-leaf Mountain Mahogany and Lodgepole Pine - Aspen, respectively) only have 1 point. This is fine as we are not really interested in these types. In fact, we are really only interested in the set of types with at least 1000 ha in the study area. 

```{r}
data4 = data2[data2$cover %in% c(9,11,14,15,17,19,24,25,26)==TRUE,]
# subset the data for regressions
# line 1 for focal types, line 2 for all types
pl = ggplot(data4, aes(x=tpi, y=ccavg)) + geom_point(alpha=0.5, col="blue") +
#pl = ggplot(data2, aes(x=tpi, y=ccavg)) + geom_point(alpha=0.5, col="blue") +    
    ggtitle(paste("Average Canopy Cover of Focal Cover Types")) +
        theme(axis.title.x = element_text(size=20, vjust=-1), 
          axis.title.y = element_text(size=20, vjust=2), 
          axis.text.x = element_text(size=16),
          axis.text.y = element_text(size=16),
          plot.title = element_text(size=20, vjust=2),
          plot.margin = unit(c(1,1,1,1), "cm")) 
    
# each cover type separately (facet)
pl + facet_wrap(~covertypes, ncol= 3) + geom_smooth(method='lm', col="black") +
    ylab("Canopy Cover Average") + xlab("Topographic Position Index Value") + theme_bw() +
     theme(axis.title.x = element_text(size=20, vjust=-1), 
          axis.title.y = element_text(size=20, vjust=2), 
          axis.text.x = element_text(size=16),
          axis.text.y = element_text(size=16),
          plot.title = element_text(size=20, vjust=2),
          plot.margin = unit(c(1,1,1,1), "cm"))  +
    theme(strip.text.x = element_text(size = 20))

# facet but only for smcm and smcx

data5 = data2[data2$cover %in% c(24,26)==TRUE,]
# subset the data for regressions
pl = ggplot(data5, aes(x=tpi, y=ccavg)) + geom_point(alpha=0.5, col="blue") +
    ggtitle(paste("Average Canopy Cover of Focal Cover Types")) +
        theme(axis.title.x = element_text(size=20, vjust=-1), 
          axis.title.y = element_text(size=20, vjust=2), 
          axis.text.x = element_text(size=16),
          axis.text.y = element_text(size=16),
          plot.title = element_text(size=20, vjust=2),
          plot.margin = unit(c(1,1,1,1), "cm")) 
    
# each cover type separately (facet)
pl + facet_wrap(~covertypes, ncol= 3) + geom_smooth(method='lm', col="black") +
    ylab("Canopy Cover Average") + xlab("Topographic Position Index Value") + theme_bw() +
     theme(axis.title.x = element_text(size=20, vjust=-1), 
          axis.title.y = element_text(size=20, vjust=2), 
          axis.text.x = element_text(size=16),
          axis.text.y = element_text(size=16),
          plot.title = element_text(size=20, vjust=2),
          plot.margin = unit(c(1,1,1,1), "cm"))  +
    theme(strip.text.x = element_text(size = 20))
```

Next we can subset the data and run separate simple linear regression on each.

```{r}
PlotLevels2 = sort(unique(data4$cover))
# make a list to store subsetted data
data.cov = vector("list", 9)
n = 1
for(i in PlotLevels2){
    data.cov[[n]] = subset(data2, cover==i, select=c(tpi, ccavg, cover))
    n = n+1
}
```

```{r}
data.lms = vector("list", 9)
for (i in 1:9){
    data.lms[[i]] = lm(ccavg~tpi, data.cov[[i]])
}

data.lms[[3]]$coefficients
```

Using the standard plotting function
```{r}
newcovertypes = c('MEG_M','MEG_X','OCFW','OCFW_U','RFR_M','RFR_X','SMC_M','SMC_U','SMC_X')
i=1
for(i in 1:length(PlotLevels2)){
    plot(data.cov[[i]]$tpi, data.cov[[i]]$ccavg, xlab="TPI", ylab="Average Canopy Cover", main=paste("Effect of TPI on average canopy cover \n during simulation for", newcovertypes[i]))
    MinMaxi = range(data.cov[[i]])
    MyDatai <- data.frame(tpi=
                seq(from = MinMaxi[1],
                to   = MinMaxi[2],
                length=10))  
    Pi <- predict(data.lms[[i]], newdata = MyDatai)
    lines(MyDatai$tpi, Pi, lty=1,col="black",lwd=2)
    #legend("topright", legend=newcovertypes[i])
}
```


ggplot version of the plots
This worked 07-01-2015
```{r}
require(grid)
n=1
for(i in PlotLevels2){
    data3 = subset(data2, data2$cover==i)
    coefs = data.lms[[n]]$coefficients
    p1 = ggplot(data3, aes(x=tpi, y=ccavg, )) + geom_point(colour="blue", alpha=0.5, size=3) + theme_bw() + 
        scale_fill_hue(c=45, l=80) + 
        ggtitle(paste("Average Canopy Cover for", data3$covertypes[1], "During Simulated Historic Period" )) +
        theme(axis.title.x = element_text(size=20, vjust=-1), 
          axis.title.y = element_text(size=20, vjust=2), 
          axis.text.x = element_text(size=16),
          axis.text.y = element_text(size=16),
          plot.title = element_text(size=20, vjust=2),
          plot.margin = unit(c(1,1,1,1), "cm"))

    p2 = p1 + ylab("Canopy Cover Average") + xlab("Topographic Position Index Value") +
        geom_abline(intercept=coefs[1], slope=coefs[2], size=2) +
        scale_y_continuous(limits = c(0,100)) +
        scale_x_continuous(limits = c(-300,300))
    print(p2)
    n = n+1
    }



```


```{r}
PlotLevels2 = sort(unique(data3$cover))
temp = lm(ccavg~tpi, data2[data2$cover==9,])
```

Making the table...
```{r}
table = read.table("/Users/mmallek/Tahoe/R/cover_tpi.txt", header=TRUE, sep=',')
subtable = table[table$Cover.Type %in% c(9,11,14,15,17,19,24,25,26)==TRUE,]
subtable$TPI.Min.CC = 0
subtable$TPI.Max.CC = 0
subtable$CC.Perc.Delt = 0
subtable$CovName = newcovertypes

#subtable$TPI.Min.CC[1] = data.lms[[1]]$coefficients[[1]] + subtable[subtable$Cover.Type==9,]$TPI.Min * data.lms[[1]]$coefficients[[2]]

for(i in 1:length(PlotLevels2)){
    subtable$TPI.Min.CC[i] = data.lms[[i]]$coefficients[[1]] + 
                                subtable$TPI.Min[i] * data.lms[[i]]$coefficients[[2]]
    subtable$TPI.Max.CC[i] = data.lms[[i]]$coefficients[[1]] + 
                                subtable$TPI.Max[i] * data.lms[[i]]$coefficients[[2]]
    subtable$CC.Perc.Delt[i] = (subtable$TPI.Max.CC[i] - subtable$TPI.Min.CC[i])/subtable$TPI.Min.CC[i]
    subtable$CC.Change[i] = subtable$CC.Perc.Delt[i] * 100
}
subtable
write.table(subtable, file="/Users/mmallek/Tahoe/RMLands/results/results20150904/tpi/cctable.txt", sep='\t')
write.csv(subtable, file="/Users/mmallek/Tahoe/RMLands/results/results20150904/tpi/cctable.csv")


```


